### 2013-11-06 proposal/proposal/chapter2.tex
Changes

    \section{Community of Web Services}\label{sec:CommunityWS}

        \subsection{Web Services}\label{sec:BRWS}

        \subsection{Definition}\label{sec:CWSDefinition}

@@

        Suppose that the land is owned by a single person, the \emph{landowner}. We refer to the other people as \emph{workers}. In this case we have the following game model:

        \begin{itemize}
        \item \emph{Players} The landowner and the $m$ workers.
        \item \emph{Actions} A coalition consisting solely of workers has a single action in which no member receibes any output. The set of actions of a coalition $S$ consisting of the landowner and $k$ workers is the set of all $S$-allocations of the output $f(k+1)$ among the members of $S$.
        \item \emph{Preferences} Each player's preferences are represented by the amount of output he obtains.
        \end{itemize}

>>>>

In this chapter, we briefly review web services, then we introduce the concept of communities of web services, their architecture and applications and the benefits of forming communities. Then we discuss the cooperative game theory concepts used throughout our research work. Finally, we discuss the relevant related work on web service communities and games in service oriented computing literature.

    \section{Community of Web Services}\label{sec:CommunityWS}
    In this section, we discuss the concept of communities of web services, and we discuss the architecture and operations of community members.

        \subsection{Web Services}\label{sec:CWSWebServices}
        Over the past years, online services have become part of standard daily life of people around the globe. Many applications these days rely on 
        web services from different providers to function. Most modern computer applications, specially 
        mobile and tablet applications which have limited storage and processing power
        are merely just an interface aggregating different information from online service providers.
        Examples are vast, weather forecasting, ticket selling, local maps and places search, shopping apps, almost all rely on
        robust web service providers.

        The World Wide Web Consortium (W3C) defines web services as follows: "software
        system designed to support interpretable machine-to-machine interaction over a network.
        It has an interface described in a machine-processable format (specifically WSDL). Other
        systems interact with the web service in a manner prescribed by its description using
        SOAP messages, typically conveyed using HTTP with XML serialization in conjunction
        with other Web-related standards". When developers declare a new web service, it will
        be discovered based on its description that fully describes the service. Developers also
        have to declare a public interface and a readable documentation to help other developers
        when integrating different services \cite{w3cwsdl}. Nowadays Web API standards which do not 
        require XML-based web service protocols like SOAP and WSDL are also emerging. They are also called 
        REST (representational state transfer) services which are moving towards simpler communication protocols.
        They are not restricted to XML formats, recently JSON, a human readable and simpler format is becoming popular among online service providers.

        We are not going to delve into engineering details of online web service implementation and its protocols in this proposal. 
        We consider the service, web services provide as a request-response operation, where they receive a message specifying a question, 
        based on this message they generate a response, satisfying end users' need. Service providers usually charge end users for services they provide,
        gaining profit in the process. For example Google has listed their pricing and plans for wide range of services they provide
        on their web service console page\footnote{https://code.google.com/apis/console}.

        In our research work, we abstract web services as rational entities\footnote{The term 
        rational is used here in the sense that web services are utility
        maximizers} providing services to end users. They aim to maximize
        their individual income by receiving enough requests from end
        users. In order to increase their revenue, web services seek for
        more tasks if they have the capacity and throughput to do so. Web
        services can join communities to have better efficiency by
        collaborating with others, to have access to higher market share,
        and to have opportunity of receiving a bigger task pool from end
        users. Also the high reliance on web services, has increased quality expectations from end users.
        Communities of web services can provide higher performance, reliability, fail recovery for end users.

        \subsection{Definition}\label{sec:CWSDefinition}
        Community in dictionary definition refers to "the condition of sharing or having certain attitudes and interests in common" or "a group of people living in the same place or having a particular characteristic in common". In \cite{DBLP:journals/internet/BenatallahSD03, Zeng:2003:QDW:775152.775211} introduce community of web services as collection of cooperative web services with a common service and functionality but different QoS metrics. Therefore $communities$ are differentiated from $composition$ type of web service cooperation in which web services with different functionalities work together to generate a new service provider with composite functionality.

@@

        In this game, land is owned by a single person, the \emph{landowner}. We refer to the other people as \emph{workers}. In this case we have a game there the set of players are the landowner and the $m$ workers, possible actions for coalitions with only workers would be distributing the zero output for all where no member receives any output. The set of actions of a coalition $S$ consisting of the landowner and $k$ workers would be the set of all $S$-allocations of the output $f(k+1)$ among the members of $S$. The preference of each player would be the amount of out she obtains.
